SunPy - Python for Solar Physics

### 2014-01-30 3-2-HEK.tex
removed orphan sentence
all hail the SSW overlords

The ability to use comparison and logical operators on HEK attributes allows 
the construction of queries of almost arbitrary complexity. 
The results of a HEK query can be used to download the 
corresponding data from the VSO using SunPy's \texttt{H2VClient}.
%schriste - this is a weird way to end this section, either show how it is done or 
% do not mention it, i think.
%dps - I agree.
%JI - I agree
%Stuart: Will do on my next pass
%ays: hmm, still nothing?

>>>>

The ability to use comparison and logical operators on HEK attributes allows 
the construction of queries of almost arbitrary complexity. 
The results of a HEK query can be used to download the 
corresponding data from the VSO using SunPy's \texttt{H2VClient}, as 
demonstrated in Listing~\ref{code:hek2vso}
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
>>> from sunpy.net import hek2vso
>>> h2v = hek2vso.H2VClient()
>>> vso_results = h2v.translate_and_query(result[0])
>>> h2v.vso_client.get(vso_results[0]).wait()
\end{minted}
\caption{Code snippet continuing from Listing~\ref{code:hek:or} showing the 
query and download of data from the first HEK result from the VSO.}
\label{code:hek2vso}
\end{listing}

### 2014-01-30 acknowledgements.tex
all hail the SSW overlords

\section{Acknowledgements}
Many of the larger features in SunPy have been developed with external support. 
Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
Summer of Code In Space (SOCIS) program, as well as a prototyped GUI and 
N-Dimensional datatype implementations. In 2013 with support from Google's 
Summer Of Code (GSOC) program, through the 
\href{http://www.python.org/psf/}{Python Software Foundation} (PSF), the 
\texttt{helio}, \texttt{hek2vso} and \texttt{database} subpackages were 
developed.The Spectra and Spectrogram classes were implemented with support 
from by the Astrophysics Research Group at Trinity College Dublin, Ireland, in 
2012.

>>>>

\section{Acknowledgements}
Many of the larger features in SunPy have been developed with external support. 
Initial development of SunPy's VSO and HEK implementations were funded by ESA's 
Summer of Code In Space (SOCIS) program, as well as a prototyped GUI and 
N-Dimensional datatype implementations. In 2013 with support from Google's 
Summer Of Code (GSOC) program, through the Python Software Foundation, the 
\texttt{helio}, \texttt{hek2vso} and \texttt{database} subpackages were 
developed.The Spectra and Spectrogram classes were implemented with support 
from the Astrophysics Research Group at Trinity College Dublin, Ireland, in 
2012.
